Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-04-10 Moltres.tex
Add passage describing how group constants are generated.
Remove single channel results. May restore later perhaps.

\section{Model Description}

@@

with the last term representing the effect of fuel advection.

\FloatBarrier
\clearpage
\printglossary[type=\acronymtype]
%% \bibliographystyle{unsrt}
%% \bibliography{Moltres}
\end{document}

>>>>

\section{Governing Equations}

@@

with the last term representing the effect of fuel advection. The governing
equation for the temperature is given by:

\begin{equation}
  \rho_fc_{p,f}\frac{\partial T_f}{\partial t} + \nabla\cdot\left(\rho_f c_{p,f}
  \vec{u}\cdot T_f -k_f\nabla T_f\right) =  Q_f
  \label{eq:fuel_temp}
\end{equation}

in the fuel and by:

\begin{equation}
  \rho_gc_{p,g}\frac{\partial T_g}{\partial t} + \nabla\cdot\left(-k_g\nabla T_g\right) =  Q_g
  \label{eq:moderator_temp}
\end{equation}

in the moderator. $Q_f$ is defined by:

\begin{equation}
  Q_f = \sum_{g=1}^G \epsilon_{f,g}\Sigma_{f,g}\phi_g
  \label{eq:fuel_source}
\end{equation}

and $Q_g$ is equal to $\gamma Q_f$, representing heat dissipation by gamma and
neutron irradiation in the moderator.

Group constants are generated with either Serpent \cite{leppanen_serpent_2015}
or Scale \cite{dehart_reactor_2011}. Temperature vs group constant interpolation
tables are constructed separately for fuel and moderator regions.

\section{Results \& Discussion}

\FloatBarrier
\clearpage
\printglossary[type=\acronymtype]
\bibliographystyle{unsrt}
\bibliography{Moltres}
\end{document}
